Test data

### 2022-07-19 Shiny/Test/Flexdashboard rows.Rmd
Fundraising ROI.

@@

    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "success",
        color = "success",
        icon = "fas fa-coffee"
      )
    })

>>>>

    # Creating Fundraising ROI value
    KPI_fundraising <- reactive({
      exceldata() |> 
          mutate(
    KPI_admin =
      str_c(
        format(
        ((revenue_private_contributions +                  revenue_membership_fees) / expenses_fundraising * 100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()
    })

@@

    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_fundraising(),
        caption = "success",
        color = "success",
        icon = "fas fa-coffee"
      )
    })

### 2022-07-19 Shiny/Test/Test data.Rmd
Fundraising ROI.

### Fundraising ROI
```{r}
kreft_excel |> 
  mutate(
    KPI_ROI = expenses_fundraising / (revenue_private_contributions + revenue_membership_fees)
  ) |> 
  select(year, KPI_ROI)
```

>>>>

### Fundraising ROI
```{r}
kreft_excel |> 
  mutate(
    KPI_ROI = expenses_fundraising / (revenue_private_contributions + revenue_membership_fees)
  ) |> 
  select(year, KPI_ROI)

kreft_excel |> 
          mutate(
            KPI_fundraising =
              str_c(format((revenue_private_contributions +                  revenue_membership_fees) / expenses_fundraising) * 100, digits = 3
          ), "%"
         ) |> 
  filter(year == max(year)) |> # selecting latest available year
             select(KPI_fundraising) |> 
        str_flatten() # turning into a single string

kreft_excel |> 
  mutate(
    KPI_admin =
      str_c(
        format(
        ((revenue_private_contributions +                  revenue_membership_fees) / expenses_fundraising * 100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()

(kreft_excel$revenue_private_contributions + kreft_excel$revenue_membership_fees) / kreft_excel$expenses_fundraising
